\huge A Usability Evaluation of Tor Launcher

### 2016-11-07 pets2017-paper/pets2017-paper.tex
mark demographics red to remember to redo

\subsection{Recruitment}
We recruited people from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}, which linked an presecreening survey that collected demographics (Appendix~\ref{qualitative-prescreening}). We pre-screened~\cite{screening} for diversity in gender, age, technical expertise, use of security tools, and familiarity with Tor in a small participant pool. Of our 16 recruited participants, 53.3\% were male. Ages ranged from 20 to~62 years ($\mu = 24.5$, $\sigma = 12.6$). 93.3\% of our participants had college education. We took participants' self-reported familiarity with technical terms use of security tools with skepticism (Appendix~\ref{prescreening-responses}). We verified their self-reported familiarity with Tor Browser in-person, and found that 4 used it, 5 heard of it but not used it, and the remaining 8 never heard of or used it.

@@

Of our recruited 124 participants, 56.8\% were male. Ages ranged from 18 to~68 years ($\mu = 28.9$, $\sigma = 12$). 56.8\% were male. 84.8\% of our participants had a college education. We distributed participants evenly across experimental condition, about 20 in each interface and environment combination. Although there is variation in gender and age in each experimental condition, we ensured each condition had about half Craiglist recruited participants and half <redacted lab>  pool participants.

>>>>

\subsection{Recruitment}
We recruited people from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}, which linked an presecreening survey that collected demographics (Appendix~\ref{qualitative-prescreening}). We pre-screened~\cite{screening} for diversity in gender, age, technical expertise, use of security tools, and familiarity with Tor in a small participant pool. {\color {red} Of our 16 recruited participants, 53.3\% were male. Ages ranged from 20 to~62 years ($\mu = 24.5$, $\sigma = 12.6$). 93.3\% of our participants had college education.} We took participants' self-reported familiarity with technical terms use of security tools with skepticism (Appendix~\ref{prescreening-responses}). We verified their self-reported familiarity with Tor Browser in-person, and found that 4 used it, 5 heard of it but not used it, and the remaining 8 never heard of or used it.

@@

{\color {red} Of our recruited 124 participants, 56.8\% were male. Ages ranged from 18 to~68 years ($\mu = 28.9$, $\sigma = 12$). 56.8\% were male. 84.8\% of our participants had a college education.} We distributed participants evenly across experimental condition, about 20 in each interface and environment combination. Although there is variation in gender and age in each experimental condition, we ensured each condition had about half Craiglist recruited participants and half <redacted lab>  pool participants.
